---
title: "Endometriosis Interview Analysis"
output:
  html_document: default
classoption: landscape
fontsize: 14pt

---
```{r libs, echo=FALSE, message=FALSE, include=FALSE}
source("/Users/nicolenisbett/Documents/PhD/R/Supreme/global.R")
library(gridExtra)

```

```{r functions, echo=FALSE, message=FALSE, include=FALSE, cache=TRUE}
endo.file=read_csv("/Users/nicolenisbett/OneDrive - University of Leeds/PhD/Data/Surveys/EndoInterview.csv")
#names(endo.file)=c("Message", "Message", "Message")
#endo.file=rbind(endo.file[,1], endo.file[,2], endo.file[,3])
endo.comments=get_comments(endo.file, "Endo")
#endo.hours=get_hours_fb(endo.file, "VisitorVisaComments")
#endo.dates=get_dates_fb(endo.file, "VisitorVisaDebate")
endo.corpus=clean_corpus(prep_corpus(endo.comments))
endo.corpus.df=get_corpus_df(endo.corpus)
endo.frequencies=term_stats(endo.corpus)
endo.dtm=get_dtm(endo.corpus)
endo.dtm.bigram=get_dtm_bigram(endo.corpus)

ud_model <- udpipe_download_model(language = "english")
ud_model <- udpipe_load_model(ud_model$file_model)
endo.ud=get_ud_data(endo.comments)
endo.8topics=get_topic_model(endo.dtm, 5)
endo.8topics.bigram=get_topic_model(endo.dtm.bigram, 5)
endo.idf = get_topic_idf(endo.8topics, endo.comments)


#endo.readability=get_readability(endo.comments)
#endo.ages=estimate_ages(endo.ud, endo.readability)

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This report gives a brief summary of the textual analysis of the KD Interview on Endometriosis.


## Frequency Analysis

The most common adjectives, phrases and pairs of words are displayed below. 
```{r frequencies, echo=FALSE,  tidy=TRUE, fig.width=10}
{grid.arrange(display_adjectives(endo.ud, 10), display_keywords(endo.ud, 10), ncol=2)}
```



A network of the most frequent consecutive word pairs (bigrams) is shown below. 


```{r bigrams, echo=FALSE, tidy=TRUE, fig.width=15, fig.height=10}
display_bigrams(endo.comments, 1, "Endo Interview")

```


***

## Topic Extraction

A plot of words most associated with one of 3 topics are shown below. 
<!---
A brief summary of those topics are:

Topic Number  | Common bigrams
-------- | ------------------
Topic 1  | mental health, blood sugars, life saving, self fund
Topic 2  | complete ban, trail hinting,
Topic 3  | funding needed, psychological support, available prescription, avoiding complications
Topic 4  | adult care, self management, managing condition
Topic 5  | long term, daughter diagnosed
Topic 6  | closed loop system, medical conditions, change diet, diabetes team
Topic 7  | healthcare, newly diagnosed
Topic 8  | basal insulin, checking blood, development type, weight gain
Topic 9  | postcode lottery, mental health, urine test
Topic 10  | nodeal brexit, quality of life, reassuring people, manage condition
--> 

<!---\begin{center}
\end{center}
![](Diabetes bigram topics.pdf)  


\begin{center}
\includegraphics{Diabetes bigram topics.pdf}
\end{center}
--> 

```{r, echo=FALSE, message=FALSE}
#display_top_topics(endo.8topics, 5, "Endo Interview")

endo.idf %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(Topic) %>% 
  top_n(10) %>% 
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill = as.factor(Topic))) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~Topic, ncol = 4, scales = "free") +
  coord_flip()

```

<!--
```{r twordcloud, echo=FALSE, message=FALSE, warning=FALSE}
myColourHue= function(n=10) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 45, c = 100)[1:n]
}
get_topic_wordcloud(endo.8topics)
```
-->



Topic model visualisations are split into two sections:

  * **Left** - showing topic distances from each other based on the types of words in each,

  * **Right** – showing the top 30 words in each topic (red bar) and overall in the dataset (blue bar). I recommend setting the relavance metric to 0.6 to get a more representative list of words in each topic.

This visualisation is interactive, hover over each topic number to view the words in each topic, or select each word to view which topics it appears.  

https://nicolednisbett.github.io/#topic=0&lambda=0.6&term=
<!--
```{r servis, echo=FALSE, message=FALSE, warning=FALSE}
serVis(topicmodels2LDAvis(endo.8topics), out.dir="a", open.browser = FALSE)
htmltools::includeHTML("a/index.html")
```

<head>
  <script src="a/d3.v3.js"></script>
  <script src="a/ldavis.js"></script>
  <link rel="stylesheet" type="text/css" href="a/lda.css">
</head>
<body>
  <div id = "mydiv"></div>
  <script>
    var vis = new LDAvis("#mydiv", "lda.json");
  </script>
</body>


<iframe width="1000" height="800" src="a/index.html" frameborder="0"></iframe>

-->


## Sentiment Analysis

The wordcloud below gives the most popular words associated with positive and negative sentiments in the survey. Specific comments
which are associated with the most popular sentiments are listed below.

```{r swordcloud, echo=FALSE, message=FALSE, warning=FALSE}
get_sentiments_wordcloud(get_bingnrc_word_frequencies(endo.corpus.df, "bing"), "bing")
```



The  **NRC** sentiment lexicon uses categorical scale to measure 2 sentiments (positive and negative), and 8 emotions (anger, anticipation, disgust, trust, joy, sadness, fear, and suprise).
Examples of words and comments in these sentiment categories are below. In this interview, the majority of submissions were *trust* but also categorised as *anticipation*, *positive* and *joy*. 

```{r nrc2, echo=FALSE, message=FALSE}
  plot_bingnrc_distributions(get_bingnrc_document_frequencies(endo.corpus,"nrc"), "Endo Interview", "nrc")
  
```


Hover over the plot below to read the content of the comments within each sentiment category.

```{r comments,echo=FALSE, message=FALSE, warning=FALSE }
ggplotly(display_topic_comments(get_sentiment_comments(endo.corpus.df, endo.comments, "nrc"), "Endo Interview"), width=1000, height = 600) %>% config(displayModeBar=FALSE) %>% hide_legend()
```


***


An example of a comment categorised as **anticipation**

  > `r endo.comments[4,][[1]]`

An example of a comment categorised as **positive**

  > `r endo.comments[11,][[1]]`

An example of a comment categorised as **trust**

  > `r endo.comments[5,][[1]]`

An example of a comment categorised as **joy**

  > `r endo.comments[7,][[1]]`

An example of a comment categorised as **negative**

  > `r endo.comments[17,][[1]]`
